% LaTeX Template
% Version 1.1 (9/21/2016)
%
% Original author:Douglas Rudolph 
% (http://DougRudolph.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Doug}{Rudolph}{ \urlstyle{same}\url{http://DougRudolph.com} \\
\href{mailto:drudolph914@gmail.com}{drudolph914@gmail.com} | 973.271.6231
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Rutgers University}
\descript{Computer Science}
\location{Expected Graduation: May 2017 \\ Location: Piscataway, NJ}
\sectionsep


\descript{BA in Computer Science}
\location{Expected May 2017 | Piscatawy, NY}
Conc. in Computer Graphics \\
College of Arts and Sciences \\
\location{ Cum. GPA: 3.96 / 4.0 \\
Major GPA: 4.0 / 4.0}
\sectionsep

\subsection{La Martiniere for Boys}
\location{Grad. May 2011|  Kolkata, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/11}
{\custombold{11}} \\
LinkedIn://  \href{https://www.linkedin.com/in/DougRudolphJr}{\custombold{DouglasRudolphJr}} \\
YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\custombold{DeedyDash007}} \\
Twitter://  \href{https://twitter.com/debarghya_das}{\custombold{@debarghya\_das}} \\
Quora://  \href{https://www.quora.com/Debarghya-Das}{\custombold{Debarghya-Das}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Advanced Machine Learning \\
Open Source Software Engineering \\
Advanced Interactive Graphics \\
Compilers + Practicum \\
Cloud Computing \\
\sectionsep

\subsection{Undergraduate}
Information Retrieval \\
Operating Systems \\
Artificial Intelligence + Practicum \\
Functional Programming \\
Computer Graphics + Practicum \\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
Unix Tools and Scripting \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
Java \textbullet{} C\# \textbullet{} Python \textbullet{} C++ \\
C\textbullet{} ASP.net \textbullet{} JavaScript \\ 
\location{Over 1000 lines:}
Bash\textbullet{} CSS \textbullet{} \LaTeX\ \textbullet{} Assembly \\
\location{Familiar:}
Android \textbullet{} OpenGL \textbullet{} MySQL
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Reccelerator}
\descript{| Software Engineer \& Co Founder}
\location{Expected July 2014 – Now | Washington DC, MD \& Sparta, NJ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Wrote a web payment portal using C\#, ASP.net, and the Stripe payment API \\to track and store credit card transactions in a Microsoft SQL Database.
\item Developed an in house data-analytics API with the the C\# LINQ framework \\to pull statistics from credit card transactions and spending patterns. 
\item All code was reviewed, perfected, and pushed to production.
\end{tightemize}
\sectionsep

\runsubsection{Rutgers University}
\descript{| Graphics Researcher}
\location{May 2016 – Now | Piscataway, NJ}
\begin{tightemize}
\item Work underneath Ph.D Dr. Bahman Kalantari as a developer on his polynomiogrpahy graphics research that generates algorithmic images.  
\item Developed a multiplatform application that visualizes Dr. Kalantari's solution \\ to the Convex Hull problem for Android, iOS, HTML, and Desktop. 
\end{tightemize}
\sectionsep

\runsubsection{Rutgers University}
\descript{| Recitation Leader \& Code Red Tutor}
\location{Sep 2016 – Now | Piscataway, NJ}
\begin{tightemize}
\item Organize and teach weekly recitations as well as answer questions to solidify concepts that are taught during formal lectures. 
\item Code Red is a tutoring service where incoming CS students can meet once a week with a qualified upperclassman that offer one-on-one tutoring in Introduction to CS through Java - 111 as well as Design \& Analysis of Algorithms - 112. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Base-is}
\descript{| Base Detection Visualization}
\location{https://www.github.com/11/Base-is}
Worked with and to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  Publication submitted.
\sectionsep

\runsubsection{GG-Engine}
\descript{| 2D Java Platformer Game Engine}
\location{https://www.github.com/11/GG-engine}
Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
\sectionsep

\runsubsection{TimeStamp}
\descript{| Speed Running Splits Timer}
\location{https://www.github.com/11/TimeStamp}
Lead the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. Publication submitted.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Involvement} 
\begin{tabular}{rll}
2014	     & top 52/2500  & KPCB Engineering Fellow\\
2014	     & 2\textsuperscript{nd} most points  & Google Code Jam, Qualification Round\\
2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
2013	     & National  & Jump Trading Challenge Finalist\\


\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

\begin{tabular}{rll}
2014 	& top 12\%ile    & Tau Beta Pi Engineering Honor Society\\
2014   & National   & The Global Leadership and Education Forum (tGELF)\\
2012   &  National  & Golden Key International Honor Society\\
2012   &  National   & National Society of Collegiate Scholars\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
